\bf The forestecology R package for fitting and assessing models of interspecies competitive effects on the growth of trees

### 2021-02-23 paper/forestecology.Rmd
second small push

The `forestecology` package attempts has the following two ecological goals: 1) to evaluate the effect of competitor species identity using permutation tests and 2) to evaluate model performance using spatial cross-validation. To achieve these two goals, we outline a basic analysis sequence comprising of these four main steps:

@@

The first step in the our analysis sequence is to compute the growth of trees using data from two censuses. The `compute_growth()` function computes growth assuming census data that roughly follows ForestGEO standards. Despite such standards, minor variations will still exist between sites, thereby necessitating some data wrangling and checking. For example, the SCBI site records all DBH's in millimeters, whereas the Michigan Big Woods site records them in centimeters @andersonteixeira_ctfs-forestgeo_2015 @allen_michigan_2020.

>>>>

The `forestecology` package has the following ecological goals: 1) to evaluate the effect of competitor species identity using permutation tests and 2) to evaluate model performance using spatial cross-validation. To achieve these goals, we outline a basic analysis sequence comprising of these four main steps:

@@

The first step in the our analysis sequence is to compute the growth of trees using data from two censuses. The `compute_growth()` function computes growth assuming census data that roughly follows ForestGEO standards. Despite such standards, minor variations will still exist between sites, thereby necessitating some data wrangling and checking. For example, the SCBI site records all DBH's in millimeters @bourg_initial_2013, whereas the Michigan Big Woods site records them in centimeters @allen_michigan_2020.

### 2021-02-23 paper/forestecology.tex
second small push

While there are a littany of models one can consider, in PLOSOne we
considered a simple one.

Describe model specifics. Bayesian linear regression model.

Next we fit the following linear model to the DBH of each focal tree.
Let \(i = 1, \ldots, n_j\) index all \(n_j\) trees of ``focal'' species
group \(j\); let \(j = 1, \ldots, J\) index all \(J\) focal species
groups; and let \(k = 1, \ldots, K\) index all \(K\) ``competitor''
species groups. We modeled the growth in diameter per year \(y_{ij}\)
(in centimeters per year) of the \(i^{th}\) tree of focal species group
\(j\) as a linear model \(f\) of the following covariates
\(\vec{x}_{ij}\)

@@

The \texttt{forestecology} package attempts has the following two
ecological goals: 1) to evaluate the effect of competitor species
identity using permutation tests and 2) to evaluate model performance
using spatial cross-validation. To achieve these two goals, we outline a
basic analysis sequence comprising of these four main steps:

@@

The first step in the our analysis sequence is to compute the growth of
trees using data from two censuses. The \texttt{compute\_growth()}
function computes growth assuming census data that roughly follows
ForestGEO standards. Despite such standards, minor variations will still
exist between sites, thereby necessitating some data wrangling and
checking. For example, the SCBI site records all DBH's in millimeters,
whereas the Michigan Big Woods site records them in centimeters
\citet{andersonteixeira_ctfs-forestgeo_2015}
\citet{allen_michigan_2020}.

>>>>

While there are a litany of models one can consider, in
\citet{allen_permutation_2020} we considered a simple one.

We fit the following linear model to the DBH of each focal tree. Let
\(i = 1, \ldots, n_j\) index all \(n_j\) trees of ``focal'' species
group \(j\); let \(j = 1, \ldots, J\) index all \(J\) focal species
groups; and let \(k = 1, \ldots, K\) index all \(K\) ``competitor''
species groups. We modeled the growth in diameter per year \(y_{ij}\)
(in centimeters per year) of the \(i^{th}\) tree of focal species group
\(j\) as a linear model \(f\) of the following covariates
\(\vec{x}_{ij}\)

@@

The \texttt{forestecology} package has the following ecological goals:
1) to evaluate the effect of competitor species identity using
permutation tests and 2) to evaluate model performance using spatial
cross-validation. To achieve these goals, we outline a basic analysis
sequence comprising of these four main steps:

@@

The first step in the our analysis sequence is to compute the growth of
trees using data from two censuses. The \texttt{compute\_growth()}
function computes growth assuming census data that roughly follows
ForestGEO standards. Despite such standards, minor variations will still
exist between sites, thereby necessitating some data wrangling and
checking. For example, the SCBI site records all DBH's in millimeters
\citet{bourg_initial_2013}, whereas the Michigan Big Woods site records
them in centimeters \citet{allen_michigan_2020}.
